---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swatches

<!-- badges: start -->
<!-- badges: end -->

The goal of swatches is to give basic functions for displaying color palettes on color wheel and as swatches

## Installation

You can install the development version of swatches from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("mic-wypych/swatches")
```

## Examples

You can plot a color wheel of a palette like this:

```{r example}
library(swatches)

pal <- c("#90e0ef", "#48cae4", "#0096c7", "#023e8a")
plot_wheel(pal)

```
The resulting plot is a ggplot object so ou can add any of the typical ggplot customizations if you want like changing theme, adding titles etc.

You can plot swatches for a color palette like this:

```{r example2}
library(swatches)

pal <- c("#90e0ef", "#48cae4", "#0096c7", "#023e8a")
plot_swatch(pal, nrow = 2)

```




